---
name: Noushin Nabavi, PhD
position: "Economist"
address: "Victoria, BC"
phone: +1 778-999-1982
www: noushinn.github.io
email: "nabavi.noushin@gmail.com"
twitter: nabavinoushin
github: noushinn
linkedin: noushin-nabavi-56b27b13
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# Career Highlights

•	Results-driven, forward-thinking accomplished Research Scientist
•	Demonstrated leadership and project management experience in private and public sectors
•	Skilled quantitative analyst proficient with Python, R and Microsoft Office 
•	Experienced delivery of products including wrangled data, analytics concepts and documentation"from rigorously defensible definitions through to implementation and evaluation 
•	Service-oriented team player dedicated to delivering quality services and gaining the trust of clients and stakeholders


# Education
```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Certifications", "Data Camp", "Online", "2018-2019", "Data Analytics using R",
  "Certifications", "Mitacs Inc.", "University of British Columbia", "2017-2019", "Project Management and Agile Transformation",
  "Certifications", "Yale Centre for Integration of Teaching and Learning", "Online Summer Institute for Teaching", "2018", "Teaching best practices",
  "mini-MBA", "University of British Columbia", "Vancouver, BC, Canada", "2018", "Business Administration for Academics",
  "Doctor of Philosophy", "University of Toronto", "Toronto, ON, Canada", "2005-2011", "Cell and Systems Biology",
  "Bachelor of Science", "University of Toronto", "Toronto, ON, Canada", "2001-2005", "Honors in Cell and Molecular Biology"
  
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Professional Experiences
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Mitacs Science Policy Fellow", "BC Government", "Victoria, BC, Canada", "September 2018 - September 2019", "Analyze and communicate complex administrative integrated data for evidence based policy making; Build and strengthen effective stakeholder relationships with ministry clients and contractors; Manage a data science project while developing and implementing timely methodologies and performance metrics",
  
  "Senior Research Fellow", "University of British Columbia", "Vancouver, BC, Canada", "February 2015 - February 2018", "Assemble and lead an international consortium of scientists for a genomics project, published 5 manuscripts and presented the results in 3 international conferences and 2 local symposia; Analyze and integrate genomics, transcriptomics, and proteomics datasets using R and proprietary software; Wrote and secured a $275K operating grant from BC Cancer Foundation for next generation sequencing tumor profiling of malignant peritoneal mesothelioma",

  "Postdoctoral Fellow", "University of California, San Francisco", "San Francisco, CA, USA", "August 2013 - December 2014", "Design research project and conduct experiments related to liver disease with an expert team of scientists; Analyze experimental data and integrate results to generate presentations and publications; Contribute to securing a $427K NIH grant",

    "Postdoctoral Fellow", "University of California, Berkeley", "Berkeley, CA, USA", "January 2012 - July 2013", "Implement a reproducible scientific workflow for a project related to aging; designed and carried out experiments with animal models for aging, analyzed results; Manage a research project with graduate students and undergraduate students towards publication in a peer-review journal",

  "Teaching Assistant and Research Co-Supervisor", "University of Toronto", "Toronto, ON, Canada","September 2005 - December 2011", "Rank the top 10% among departmental teaching assistants for 500+ hours of instruction in introductory biology laboratory, cellular molecular biology, and microbiology; Create and delivere departmental lectures to 500+ students with satisfactory responses from students; Co-supervise 10 undergraduate thesis students on successful thesis projects maintaining 100% retention rate (8 students secured successful science jobs, 2 pursued graduate studie)"
  
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Awards & Achievements
## Awards
```{r}
tribble(
  ~ award, ~ from, ~ location, ~ year,
  
 "Canadian Mitacs Science Policy Fellowship", "UVic/BC Ministry of Health", "Victoria, BC", "2019-2020",   

 "Finalist team for BC Premier’s Award in Evidence-Based Design for Children and Youth Mental Health Integrated data project", "BC Ministry of Citizens' Services", "Victoria, BC", "2019",    

 "Third place for designing prosthetic hand tools at Health and Regenerative Medicine Hackathon (donation of award to Victoria Hand Project)", "University of Victoria", "Victoria, BC", "2019",   

 "People’s choice leadership award for Victoria Code.Hack health hackathon at Island Health", "Vancouver Island Hospital", "Victoria, BC", "2019",    

 "Canadian Mitacs Science Policy Fellowship", "UVic/BC Ministry of Citizens' Services", "Victoria, BC", "2018-2019",     

 "Travel award to participate and lead an analytics team at hackseq hackathon", "University of British Columbia", "Vancouver, BC", "2018-2019",    

 "Travel award to participate at UBC’s career panel discussing role of postdocs in industry", "University of British Columbia", "Vancouver, BC", "2018",    

 "Health and Regenerative Medicine Hackathon in kind value in mentorship award", "University of Victoria", "Victoria, BC", "2018",     

 "Honorable mention for Brief Policy Pitch for Indigenous reconciliation", "Institute of Public Administration", "Victoria, BC", "2018",    

 "Certificate of distinction for completing Summer Institute for Evidence-Based STEM Teaching", "The CIRTL Network", "on-line", " 2018",      

 "Entrepreneurship@UBC venture building phase 1", "University of British Columbia", "Vancouver, BC", "March-May 2018",   

 "Mitacs Accelerate Postdoctoral Fellowship Award", "University of British Columbia", "Vancouver, BC", "2015-2018", 

 "Mini-MBA award, Partnership with Graduate Management Consulting Association", "University of British Columbia", "Vancouver, BC", "2018",    

 "Rare Genomics Institute’s BeHEARD Technology Prize in partnership with Addgene", "University of British Columbia", "Vancouver, BC", "2017-2018",    

 "Travel award to attend", "American Association of Cancer Research conference", "Washington DC, USA", "2017",       
 "Amazon Web Services Cloud Research Grant", "University of British Columbia", "Vancouver, BC", "2016-2017",   

 "Science Teaching Fellowship", "American Society for Microbiology", "on-line", "2014-2015",      

 "Siebel Stem Cell Postdoctoral Fellowship", "University of California Berkeley", "California, USA", "2012-2013",

 "Graduate Student Research Award", "University of Toronto", "Toronto, ON", "July 2010",    

 "Travel Award to attend", "15th Canadian Connective Tissue Conference", "Calgary, AB", "July 2009",  

 "Natural Sciences and Engineering Research Council (NSERC)-CGS", "University of Toronto", "Toronto, ON", "May 2009-2012",     

 "Ontario Textbook and Technology Grant", "University of Toronto", "Toronto, ON", "December 2008",    

 "General Motors Women in Science and Mathematics Award", "University of Toronto", "Toronto, ON", "April 2008", 

 "Travel Award from 14th Canadian Connective Tissue Conference", "McGill University", "Montreal, QC", "June 5-7, 2008",   

 "Travel Award to attend", "47th American Society for Cell Biology", "San Diego, CA, USA", "December 2007",  

 "Queen Elizabeth II Aiming for the Top Tuition Scholarship", "University of Toronto", "Toronto, ON", "September 2001"


) %>%
  
  detailed_entries(from, location, award, year)
```

